Assessing the potential of Jacobian-free Newton-Krylov methods for cell-centred finite volume solid mechanics

### 2024-08-22 article.tex
Updates to the test cases section

\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
%\documentclass[sn-mathphys,Numbered,draft]{sn-jnl}% Math and Physical Sciences Reference Style

@@

In this work, we restrict our interest to Lagrangian formulations of the conservation of linear momentum.
Assuming small strains, the linear geometry formulation is expressed in strong integral form as:
\begin{eqnarray} \label{eqn:momentum_lingeom}
    \int_{\Omega} \rho \frac{\partial^2 \bb{u} }{\partial t^2} \, d\Omega
    =
    \oint_{\Gamma} \bb{n} \cdot \bb{\sigma} \,  d\Gamma
    + \int_{\Omega}  \rho \bb{g} \, d\Omega
\end{eqnarray}
where $\Omega$ is the volume of an arbitrary body bounded by a surface $\Gamma$ with outwards pointing normal $\bb{n}$.
The density is $\rho$, $\bb{u}$ is the displacement vector, $\bb{\sigma}_s$ is the engineering (small strain) stress tensor, and $\bb{g}$ is a body force per unit mass, e.g., gravity.

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Newton-Type Solution Methods}
%%--------------------------------------------------------------------------------------------------------------------%%
To facilitate the comparison between classic segregated solution algorithms and the proposed Jacobian-free Newton-Krylov algorithm, the governing linear momentum conservation (Equations \ref{eqn:momentum_lingeom}, \ref{eqn:momentum_TL} and \ref{eqn:momentum_UL}) is expressed in the general form:
\begin{eqnarray} \label{eqn:residual}
	\mathcal{R}(\bb{u}) = \bb{0}
\end{eqnarray}
where $\mathcal{R}$ represents the \emph{residual} (imbalance) of the equation, which is a function of the primary unknown field.
For example, in the linear geometry case, the residual is given as
\begin{eqnarray}
    \bb{R}(\bb{u})
    \;=\;
    \oint_{\Gamma} \bb{n} \cdot \bb{\sigma}(\bb{u}) \,  d\Gamma
    + \int_{\Omega}  \rho \bb{g} \, d\Omega
    -  \int_{\Omega} \rho \frac{\partial^2 \bb{u} }{\partial t^2} \, d\Omega
    \;=\; \bb{0}
\end{eqnarray}
where the dependence of the stress tensor on the solution vector is made explicitly clear: $\bb{\sigma}(\bb{u})$.

@@

%\hl{4 - globalisation}
A challenge with Newton-type methods, including Jacobian-free versions, is convergence can be poor when far from the true solution, and divergence is often a real possibility.
Globalisation refers to steering an initial solution towards the quadratic convergence range of the Newton method.
Several strategies are possible, and it is common to combine approaches \cite{Knoell2004}.
In the current work, a line search procedure is used to select the $\alpha$ parameter in the solution update step (the second line in Equations \ref{eq:NewtonRaphson}).
Line search methods assume the Newton update direction is correction and aim to find a scalar $s > 0$ that decreases the residual $\bb{R}(\bb{u}_k + s \delta \bb{u}) < \bb{R}(\bb{u}_k)$.
The scalar s is typically $\leq 1$, but extrapolation ($>1$) is also possible for accelerating convergence, albeit at the expense of robustness.

@@

% Possible cases
% Compare seg and JFNK; maybe also Abaqus, just for reference
% Show times/results for successively refined meshes
%- cantilever
%- narrowTmember
%- ellipticPlate
%- Other
%	- cooks membrane (small or large strain)
%	- necking -> Andrew's flatBar 3-D case, maybe even with his damage model?
%	- bi-material
%	- industrial case: bad/real mesh and show parallel scaling
%	- ideal ventricle (problem 2, Land et al.)
%	
%Effects that could be studied:
%- stabilisation magnitude (scaleFactor with RhieChow or alpha)
%- globalisation strategies, e.g. predictor, segregated solution, time-step, composite snes
%- parallel scaling
%- preconditioner: LU, ILU (what N?), MG (HYPRE) and linear solver
%  	- Knoll found that lagging the precondioner construction gave speed-ups: this is easy for us to try with PETSc
%	- effect of GMRES "restart": Knoll shows that lower restarts can be used with a better preconditioner
%- mesh types: uniform mesh vs large gradients in refinement; structured vs unstructured

This section assesses the performance of the proposed Jacobian-free Newton-Krylov solution approach and several benchmark cases.
The cases have been chosen to exhibit a variety of characteristics in terms of
\begin{itemize}
	\item Geometric dimension (2-D vs. 3-D),
	\item Geometric nonlinearity (small strain vs. large strain)
	\item Statics vs. dynamics, and
	\item Material behaviour (elasticity, elastoplasticity, hyperelasticity).
\end{itemize}

@@

The presented analyses aim to be extensive; however, they are not exhaustive.
Several common features of modern solid mechanics procedures, including contact mechanics and incompressibility, where mixed formulations are required, are left for future work.

@@

\hl{Here, for the selected 4-6 cases, we should describe:}
\hl{- geometry (+ image) and meshes (maybe image of one type of mesh)}
\hl{- material properties}
\hl{- loading conditions}

\hl{I suggest we aim to keep the descriptions above concise}
\hl{we can use tables where appropriate and can include the loading conditions in the geometry figure}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Accuracy and Order of Accuracy Verification}
%%--------------------------------------------------------------------------------------------------------------------%%

\hl{This should show that JFNK does not affect the answers: one case is fine}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Time and Memory Requirements}
%%--------------------------------------------------------------------------------------------------------------------%%

\hl{Present a table of time and memory for meshes and cases}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Effect of XXXX}
%%--------------------------------------------------------------------------------------------------------------------%%

\hl{There are many parameters we could examine; here are ideas}
\begin{itemize}
	\item \textbf{Mesh types}: tet, hex, poly. MAYBE. We would pick one case and show its timings and memory (and maybe compare residual convergence) for tet (Gmsh is a good option), hex and poly (Gmsh + polyDualMesh, or maybe Fluent?).
	 Alternatively, we can use different meshes for different cases in the "time and memory requirements" section, e.g. ellipticPlate could use hex, but narrowTmember uses tet. However, then it would not be clear if the differences come from the cases or the mesh.
	\item \textbf{Rhie-Chow stabilisation scaling}: MAYBE. from a quick check, the value of $s$ greatly affects the convergence of the linear solver: $s=1$ shows good convergence, $s=0.1$ is poor convergence. It might be a nice insight to show that smoothing is equally important for the linear solver and the solution stability.
	\item \textbf{Preconditioner choices}: YES: compare ILU, LU, and multigrid. This should be easy to do. We can use multigrid for all other sections (I think it will be the best), but here, we can show the differences (time and memory) for some or all of the cases and mesh densities.
	\item \textbf{Linear solver settings}: MAYBE: In GMRES, we must choose the value of the "restarts" parameter; the default in PETSc of 30 does not always seem good enough (I have been setting it to 100). We could show its affect on one case. I think the optimal choice is linked with the choice of preconditioner (a better preconditioner means we can use a small restart value) so maybe we include this with the "preconditioner choices" section.
	\item \textbf{Linear solver oversolving}: MAYBE: this can also be considered a linear solver setting. For segregated, we always use a relative tolerance of 0.1, but initial tests for JFNK show that 0.1 is too loose and 1e-3 seems better, although maybe there is no difference with using 1e-6.
	\item \textbf{The effect of globalisation strategies}: MAYBE: we could simply say that we use line search and a predictor step, or we could show their effect. Maybe pick one or more cases
	\item \textbf{Multi-CPU-core parallelisation}: YES: final sub-section
	\item \textbf{Something else?}
\end{itemize}

\hl{Let's prioritise these and complete the first few. I have added my thoughts above in CAPITALS.}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Parallelisation}
%%--------------------------------------------------------------------------------------------------------------------%%

>>>>

%\documentclass[sn-mathphys,Numbered]{sn-jnl}% Math and Physical Sciences Reference Style
\documentclass[sn-mathphys,Numbered,draft]{sn-jnl}% Math and Physical Sciences Reference Style

@@

In this work, we restrict our interest to Lagrangian formulations of the conservation of linear momentum.
Assuming small strains, the linear geometry formulation is expressed in strong integral form as:
\begin{eqnarray} \label{eqn:momentum_lingeom}
    \int_{\Omega} \rho \frac{\partial^2 \bb{u} }{\partial t^2} \, d\Omega
    =
    \oint_{\Gamma} \bb{n} \cdot \bb{\sigma}_s \,  d\Gamma
    + \int_{\Omega}  \rho \bb{g} \, d\Omega
\end{eqnarray}
where $\Omega$ is the volume of an arbitrary body bounded by a surface $\Gamma$ with outwards pointing normal $\bb{n}$.
The density is $\rho$, $\bb{u}$ is the displacement vector, $\bb{\sigma}_s$ is the engineering (small strain) stress tensor, and $\bb{g}$ is a body force per unit mass, e.g., gravity.

@@

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Newton-Type Solution Methods}
%%--------------------------------------------------------------------------------------------------------------------%%
To facilitate the comparison between classic segregated solution algorithms and the proposed Jacobian-free Newton-Krylov algorithm, the governing linear momentum conservation (Equations \ref{eqn:momentum_lingeom}, \ref{eqn:momentum_TL} and \ref{eqn:momentum_UL}) is expressed in the general form:
\begin{eqnarray} \label{eqn:residual}
	\mathcal{R}(\bb{u}) = \bb{0}
\end{eqnarray}
where $\mathcal{R}$ represents the \emph{residual} (imbalance) of the equation, which is a function of the primary unknown field.
For example, in the linear geometry case, the residual is given as
\begin{eqnarray}
    \bb{R}(\bb{u})
    \;=\;
    \oint_{\Gamma} \bb{n} \cdot \bb{\sigma}_s(\bb{u}) \,  d\Gamma
    + \int_{\Omega}  \rho \bb{g} \, d\Omega
    -  \int_{\Omega} \rho \frac{\partial^2 \bb{u} }{\partial t^2} \, d\Omega
    \;=\; \bb{0}
\end{eqnarray}
where the dependence of the stress tensor on the solution vector is made explicitly clear: $\bb{\sigma}_s(\bb{u})$.

@@

%\hl{4 - globalisation}
A challenge with Newton-type methods, including Jacobian-free versions, is convergence can be poor when far from the true solution, and divergence is often a real possibility.
Globalisation refers to steering an initial solution towards the quadratic convergence range of the Newton method.
Several strategies are possible, and it is common to combine approaches \cite{Knoell2004}.
In the current work, a line search procedure is used to select the $s$ parameter in the solution update step (the second line in Equations \ref{eq:NewtonRaphson}).
Line search methods assume the Newton update direction is correction and aim to find a scalar $s > 0$ that decreases the residual $\bb{R}(\bb{u}_k + s \delta \bb{u}) < \bb{R}(\bb{u}_k)$.
The scalar $s$ is typically $\leq 1$, but extrapolation ($>1$) is also possible for accelerating convergence, albeit at the expense of robustness.

@@

% Possible cases
% Compare seg and JFNK; maybe also Abaqus, just for reference
% Show times/results for successively refined meshes
%- cantilever -> dynamic 3-D from Zeljko paper
%- narrowTmember
%- ellipticPlate
%- spherical cavity - uniaxial, static
%- spherical cavity - dynamic, pressure
%- Other
%	- cooks membrane (small or large strain)
%	- necking -> Andrew's flatBar 3-D case, maybe even with his damage model?
%	- bi-material
%	- industrial case: bad/real mesh and show parallel scaling
%	- ideal ventricle (problem 2, Land et al.)
%	
%Effects that could be studied:
%- stabilisation magnitude (scaleFactor with RhieChow or alpha)
%- globalisation strategies, e.g. predictor, segregated solution, time-step, composite snes
%- parallel scaling
%- preconditioner: LU, ILU (what N?), MG (HYPRE) and linear solver
%  	- Knoll found that lagging the precondioner construction gave speed-ups: this is easy for us to try with PETSc
%	- effect of GMRES "restart": Knoll shows that lower restarts can be used with a better preconditioner
%- mesh types: uniform mesh vs large gradients in refinement; structured vs unstructured

This section assesses the performance of the proposed Jacobian-free Newton-Krylov solution approach on several benchmark cases.
The cases have been chosen to exhibit a variety of characteristics in terms of
\begin{itemize}
	\item Geometric dimension (2-D vs. 3-D),
	\item Geometric nonlinearity (small strain vs. large strain)
	\item Statics vs. dynamics, and
	\item Material behaviour (elasticity, elastoplasticity, hyperelasticity).
\end{itemize}

@@

The presented analyses aim to be extensive but not exhaustive.
Several common features of modern solid mechanics procedures are left for future work, including contact mechanics and incompressibility. %, where mixed formulations are required.

The remainder of this section is structured as follows:
the order of accuracy of the proposed discretisation is assessed on a 3-D linear elastic case with a known analytical solution.
This demonstrates that the predictions are unaffected by the solution algorithm choice.
Subsequently, the remaining sub-sections assess the effect of several key parameters on the Jacobian-free Newton Krylov approach, including \hl{XXX}.

@@

%\hl{Here, for the selected 4-6 cases, we should describe:}
%\hl{- geometry (+ image) and meshes (maybe image of one type of mesh)}
%\hl{- material properties}
%\hl{- loading conditions}
%\hl{I suggest we aim to keep the descriptions above concise}
%\hl{we can use tables where appropriate and can include the loading conditions in the geometry figure}

This section concisely describes the benchmark cases examined in subsequent sections.
Details of the geometry, mesh, loading conditions, material properties, and relevant numerical settings are given so that the results can be reproduced.

\paragraph{Case 1: Spherical Cavity in an Infinite Solid Subjected to Remote Stress}
This 3-D case consists of a spherical cavity with radius $a = 0.2$ m (Figure \ref{fig:spherical_cavity}) in an infinite, isotropic linear elastic solid ($E = 200$ GPa, $\nu = 0.3$).
Far from the cavity, the solid is subjected to a tensile stress $\sigma_{zz} = T = 1$ MPa, with all other stress components zero.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity.pdf} 
   \caption{Spherical cavity case geometry, mesh and loading conditions \hl{geometry + loading conditions + maybe an example mesh. Show x/y/z axes}}
   \label{fig:spherical_cavity}
\end{figure}
The analytical expressions for the stress distributions around the cavity, first derived by \cite{Southwell1926}, are
\begin{eqnarray}
	\sigma_{rr} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - \frac{r^2}{R^2} \left( 72 - 15\nu - 105 \frac{a^2}{R^2} \right) + 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right], \\
	\sigma_{\theta\theta} &=&
		\frac{T}{14 - 10\nu} \frac{a^3}{R^3}
		\left[ 9 - 15\nu - 12 \frac{a^2}{R^2}  - 15 \frac{r^2}{R^2} \left( 1 - 2\nu - \frac{a^2}{R^2} \right) \right], \\
	\sigma_{zz} &=&
		T \left[ 1 - \frac{1}{14 - 10\nu} \frac{a^3}{R^3} \left\{ 38 - 10\nu - 24 \frac{a^2}{R^2} 
		- \frac{r^2}{R^2} \left( 117 - 15\nu - 120 \frac{a^2}{R^2} \right)
		+ 15 \frac{r^4}{R^4} \left( 5 - 7 \frac{a^2}{R^2} \right) \right\} \right], \notag \\
		\\
	\sigma_{zr} &=&
	\frac{T}{14 - 10\nu} \frac{a^3 z r}{R^5}
	\left[ -3(19 - 5\nu) + 60 \frac{a^2}{R^2} + 15 \frac{r^2}{R^2} \left( 5 - 7 \frac{a^2}{R^2} \right)  \right].
\end{eqnarray}
where $r^2 = x^2 + y^2$ is the cylinderical radial coordinate, $R^2 = r^2 + z^2$ is the spherical radial coodinate, and $x$, $y$, $z$ are the Cartesian coordinates.

The solution domain is taken as one-eighth of a $1 \times 1 \times 1$ m cube centred on the sphere.
The analytical tractions are applied at the far boundaries of the domain to mitigate the effects of finite geometry.
Unstructured polyhedral meshes of varying densities are employed (\hl{state average cell widths, and number of cells in each mesh}).
A coarse mesh is shown in Figure \ref{fig:spherical_cavity}.
Initially, unstructured tetrahedral meshes were generated using the Gmsh meshing utility \cite{Gmsh}, followed by conversion to their dual polyhedral representations using the OpenFOAM \texttt{polyDualMesh} utility.

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Order of Accuracy Verification}
%%--------------------------------------------------------------------------------------------------------------------%%

This section assesses the order of accuracy of the discretisation using the spherical cavity case (case 1).
A secondary purpose is to demonstrate that the choice of solution algorithm (Jacobian-free Newton-Krylov vs segregated) does not affect the predictions, assuming iteration errors are small.

The predicted axial ($\sigma_{zz}$) stress distribution is shown in Figure \ref{fig:spherical_cavity_stress}, where the peak stress ($2.xxx$ MPa) is just over twice the applied stress ($1$ MPa).
This is in contrast to the classic 2-D circular hole in an infinite plate case, which exhibits a stress concentration factor of 3.
A further difference with the 2-D circular hole case is that the local stresses more quickly return to the distant stress state as $R$ increases, with the local stresses being proportional to $\frac{1}{R^3}$ in the 3-D case and  $\frac{1}{R^2}$ in the 2-D case.
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_stress.pdf} 
   \caption{Spherical cavity case: $\sigma_{zz}$ stress distribution \hl{use Reflect in ParaView to make a nice image}}
   \label{fig:spherical_cavity_stress}
\end{figure}

Figure \ref{fig:spherical_cavity_accuracy} shows the discretisation errors ($L_2$ and $L_\infty$) in $\sigma_{zz}$ as a function of the average cell width.
The errors can be seen to \hl{describe on the average/max error trends in graphs}.
\hl{Comment on the order of accuracy: does it show what was expected or not?}
\hl{Conclude 1: order of accuracy of the discretisation is XXX}
\hl{Conclude 2: solution algorithm does not affect the answer}
\hl{There is no need to show segregated results if they are the same: just state that they are the same}
\hl{There is no need to show time and memory requirements: leave to the next section}
\begin{figure}[htbp]
   \centering
   \includegraphics[width=0.2\textwidth]{figures/spherical_cavity_error.pdf} 
   \caption{Spherical cavity case: discretisation error as a function of average cell width \hl{disp and stress errors if we have them}}
   \label{fig:spherical_cavity_accuracy}
\end{figure}

\hl{Ideally, we would also show the displacement error: we could use Richardson extrapolation for this but this can be misleading}
\hl{The displacement solution is given at} \url{http://solidmechanics.org/Text/Chapter5_4/Chapter5_4.php}
\hl{in Sec 5.4.8, but it seems wrong (the stress zz is wrong)}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Time and Memory Requirements}
%%--------------------------------------------------------------------------------------------------------------------%%
This section presents the time and memory requirements of the proposed Jacobian-free Newton Krylov approach for several cases and mesh densities.
Time and memory requires from the classic segregated approach are given for comparison, along with the requirements from commercial finite element software Abaqus (version XXX): \hl{ask Dylan to create the Abaqus results when we are happy the paper will not change}.
The finite element approach uses a coupled solution algorithm and direct linear solver, where a Newton-Raphson method is used for resolving nonlinearities.
\hl{Take care when comparing times between different hardware}

The time and memory requirements are examined for \hl{four} cases (\hl{pick 4-5 cases with different characteristics)}:
\begin{itemize}
	\item Spherical cavity (case 1): 3-D, static, linear elastic, unstructured polyhedral mesh;
	\item Cook's membrane (case 2): 2-D, static, finite strains, elastoplastic, structured quadrilaterial mesh \hl{good option};
	\item Idealised ventricle (Case 3): 3-D, static, finite strains, hyperelasticity, structured hexahedral and prism mesh \hl{good option};
	\item \hl{ZZZ} (case 4): \hl{dynamic case}; dynamic 3-D beam
	\item \hl{these four cases cover 2-D/3-D, static/dynamic, elastic/elastoplastic, small/large strain, mesh types}: \hl{maybe add another 1 more with a different combination}
\end{itemize}

Table \ref{tab:times_memory} lists the wall clock times (time according to a clock on the wall) and maximum memory usage according to the GNU time utility.
All times and memory usage were generated using \hl{hardware details} using one CPU core.
\hl{Give details of relevant numerical settings, e.g. linear solver, preconditioner, Rhie-Chow scaling, globalisation strategy if any}.
Multi-CPU-core parallelisation is examiend in Section \ref{sec:parallelisation}.
\begin{table}[htb]
	\centering
		\begin{tabular}{llll}
			\hline
			Case & Number of Cells & Time (in s) & Memory (in MB) \\
			\hline 
			Spherical cavity & 1,234 & 345 & 1,234  \\
			Spherical cavity & 12,345 & 345 & 1,234  \\
			Spherical cavity & 123,456 & 345 & 1,234  \\
			Case 2, etc & 123,456 & 345 & 1,234  \\
			Case 3, etc & 123,456 & 345 & 1,234  \\
			Case 4, etc & 123,456 & 345 & 1,234  \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage}
	\label{tab:times_memory}
\end{table}

To highlight the effect of hardware specification, Table \ref{tab:times_memory_spec2} lists the time and memory usage for a different system: \hl{e.g. Mac M2/M3 seem to give excellent performance vs Meluxina AMD EPYC cores}.
\hl{Describe the difference, e.g. 2-3 faster but same memory usage}
\hl{Additional comments/insights, e.g. time trends are the same for both systems}
\hl{We could even include multiple systems here, e.g. Mac Studio vs Meluxina AMD vs Zagreb Intel workstation vs Intel i9/i7}
\begin{table}[htb]
	\centering
		\begin{tabular}{lllll}
			\hline
			Hardware & Case & Number of Cells & Time (in s) & Memory (in MB) \\
			\hline 
			Mac Studio, M2 Ultra & Spherical cavity & 1,234 & 345 & 1,234  \\
			Mac Studio, M2 Ultra & Spherical cavity & 12,345 & 345 & 1,234  \\
			Mac Studio, M2 Ultra & Spherical cavity & 123,456 & 345 & 1,234  \\
			Meluxina, AMD EPYC & Spherical cavity & 1,234 & 345 & 1,234  \\
			Meluxina, AMD EPYC & Spherical cavity & 12,345 & 345 & 1,234  \\
			Meluxina, AMD EPYC & Spherical cavity & 123,456 & 345 & 1,234  \\
			\hline
		\end{tabular}
	\caption{Execution times and maximum memory usage for \hl{Hardware Spec 2}}
	\label{tab:times_memory_spec2}
\end{table}

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Effect of Mesh Type}
%%--------------------------------------------------------------------------------------------------------------------%%
Pick one case and show its timings and memory for tet (Gmsh), hex and poly (Gmsh + polyDualMesh).
Conclusion: mesh type does or does not affect the performance.

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Effect of Rhie-Chow Stabilisation}
%%--------------------------------------------------------------------------------------------------------------------%%
\textbf{Rhie-Chow stabilisation scaling}: MAYBE. from a quick check, the value of $\alpha$ greatly affects the convergence of the linear solver: $s=1$ shows good convergence, $s=0.1$ is poor convergence. It might be a nice insight to show that smoothing is equally important for the linear solver and the solution stability.

Pick one case and run it for several values of $\alpha$, e.g. $1$, $0.1$, $0.01$.
Report the timings (memory is not needed) and any convergence problems.

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Linear Solver and Preditioner Choices}
%%--------------------------------------------------------------------------------------------------------------------%%

The key thing in this section is the preconditioner choice (this is a key point in the paper).
Linear solver settings and oversolving is less important: leave these two points as optional (decide later).

\textbf{Preconditioner choices}: YES: compare ILU, LU, and multigrid. This should be easy to do. We can use multigrid for all other sections (I think it will be the best), but here, we can show the differences (time and memory) for some or all of the cases and mesh densities.

\textbf{Linear solver settings}: MAYBE: In GMRES, we must choose the value of the "restarts" parameter; the default in PETSc of 30 does not always seem good enough (I have been setting it to 100). We could show its affect on one case. I think the optimal choice is linked with the choice of preconditioner (a better preconditioner means we can use a small restart value) so maybe we include this with the "preconditioner choices" section.

\textbf{Linear solver oversolving}: MAYBE: this can also be considered a linear solver setting. For segregated, we always use a relative tolerance of 0.1, but initial tests for JFNK show that 0.1 is too loose and 1e-3 seems better, although maybe there is no difference with using 1e-6.

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Effect of Globalisation Strategies}
%%--------------------------------------------------------------------------------------------------------------------%%

This one is optional: decide later.
At a minimal, we could just add a comment on the importance of this.
As a by the way, I think the default line search in PETSc may not be the best one for JFNK.

\textbf{The effect of globalisation strategies}: MAYBE: we could simply say that we use line search and a predictor step, or we could show their effect. Maybe pick one or more cases

%%--------------------------------------------------------------------------------------------------------------------%%
\subsection{Parallelisation}
\label{sec:parallelisation}
%%--------------------------------------------------------------------------------------------------------------------%%
